An Empirical Analysis of the Role of Energy in Economic Growth

### 2018-09-25 README.Rmd
Better lead identifying this as an R package.
New docs.

The `MacroGrowth` package provides sophisticated tools for fitting macroeconomic 
growth models to data. 
`MacroGrowth` has several desirable features for economic modelers:

@@

The functions in this package were developed for and used first in 
Heun et al. [-@Heun:2017].

>>>>

The `R` package `MacroGrowth` provides sophisticated tools for fitting macroeconomic 
growth models to data. 
`MacroGrowth` has several desirable features for economic modelers:

@@

The functions in this package were developed for and used first in 
[Heun et al. [-@Heun:2017]](https://doi.org/10.3390/en10020203).
